Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-02-11 paper.tex
change figure links to refs

\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \cite{fig:shabbyreal_denoising}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

@@

As can be seen in  Figure \cite{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.

>>>>

\subsection{Results}
Sample predictions from the model on the validation task are presented in Figure \ref{fig:shabbyreal_denoising}. The SSIM score indicates that these models generalize very well, though they do overcompensate for shadowing features around text, by increasing the line thickness in the prediction, resulting in a bold font.

@@

As can be seen in Figure \ref{fig:shabbyreal_denoised}, the model was able to remove a significant amount of blur, line noise, shadowing from tire tracks, and watercoloring.
